---
title: Using R for Sokal & Rohlf's Biometry
output: md_document
---

Use R and work through the Sokal and Rohlf's Biometry, 3rd edition. Create an R package for the datasets.

```{r setup, include=F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, dpi = 300, fig.path='png/')
devtools::document("r")
devtools::load_all("r")
```


# Preface

"There is remarkably little correlation between innate mathematical ability and
capacity to understand the ordinary biometric methodologies. By contrast, in
our experience a very high correlation exists between success in biometry
course and success in the chosen field of biological specialization."

# 1 | Introduction

"There are still a few legitimate fields of inquiry in which, from the nature
of the phenomena studied, statistical investigation is unnecessary. When all
animals given injections of a pathogenic organisms contract the disease, while
none of the controls fall ill, statistical testing is hardly needed. Much more
frequent, however, are investigations, such as those determining the relation
betweens smoking and heart disease, where the variability of the outcomes
necessitates statistical analysis."

# 2 | Data in biology

```{r femur_length}
hist(femur, data=aphid, breaks=seq(3.25, 4.75, 0.3), col='white', 
  xlab='Femur length, 0.1 mm', main=''
)
hist(femur, data=aphid, breaks=seq(3.25, 4.75, 0.1), add=T, col=1, border='white')
```

Twenty-five femur lengths of stem mothers of the aphid _Pemphigus
populitransversus_ in 0.1 mm.


```{r pigeon_width}
par(mfrow=c(1, 2))
hist(width, data=pigeon, main='', xlab='Interorbital width, mm', ylim=c(0, 15))
hist(log10(width), data=pigeon, main='', xlab=expression(log[10]*'(Interorbital width)'), ylim=c(0, 15))
```

Interorbital width of a 40 domestic pigeons (left) and the same data log~10~ transformed (right).


# 3 | Handling of data

"The availability of computers relieves the tedium of computation, but not the
necessity to understand the methods being employed."
